### 2013-09-28 Publications/2013-ISBI14/03-methods.tex
Adapted to exact ISBI layout

\paragraph{\Gls*{fmb}} As it was previously described,
this family of correction technologies infer a \gls*{vsm}
from the phase difference map. In this work, we use the
tool \texttt{fugue} \cite{jenkinson_fsl_2012} aforementioned.

\paragraph{\Gls*{reb}} We use the tool
\texttt{topup} from \cite{jenkinson_fsl_2012} to correct
using the B0 of a reverse-encoding simulation of the \gls*{dti}.
In this second case, the \gls*{vsm} is inferred from the
differences between the two corresponding B0. This technique
also uses least-squares-fitting to interpolate the undistorted
signal, and therefore provides with a robust dropout correction.

\paragraph{\Gls*{t2b}} For this last methodology
we fine-tuned the \texttt{ANTs} tool \cite{avants_ants:_2013},
in order that registering the B0 to the T2. Additionally,
undistorted images are corrected for dropout using the determinant
of the Jacobian of the deformation field.

>>>>

\paragraph*{\Gls*{fmb}} As it was previously described,
this family of correction technologies infer a \gls*{vsm}
from the phase difference map. In this work, we use the
tool \texttt{fugue} \cite{jenkinson_fsl_2012} aforementioned.

\paragraph*{\Gls*{reb}} We use the tool
\texttt{topup} from \cite{jenkinson_fsl_2012} to correct
using the B0 of a reverse-encoding simulation of the \gls*{dti}.
In this second case, the \gls*{vsm} is inferred from the
differences between the two corresponding B0. This technique
also uses least-squares-fitting to interpolate the undistorted
signal, and therefore provides with a robust dropout correction.

\paragraph*{\Gls*{t2b}} For this last methodology
we fine-tuned the \texttt{ANTs} tool \cite{avants_ants:_2013},
in order that registering the B0 to the T2. Additionally,
undistorted images are corrected for dropout using the determinant
of the Jacobian of the deformation field.
